Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2020-12-21 manuscript.tex
Merge branch 'master' of github.com:habi/zmk-tooth-cohort-method-manuscript [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/e86b7b945d34bfb2bc29a33ed411d2caaf763c63.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/e86b7b945d34bfb2bc29a33ed411d2caaf763c63/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/436042112

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...ede04890238d3d0cc4f5748bf1fa389b1dd606b3}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/ede04890238d3d0cc4f5748bf1fa389b1dd606b3/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/ede04890238d3d0cc4f5748bf1fa389b1dd606b3}{habi/zmk-tooth-cohort-method-manuscript@ede0489}
on December 21, 2020.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...e86b7b945d34bfb2bc29a33ed411d2caaf763c63}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/e86b7b945d34bfb2bc29a33ed411d2caaf763c63/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/e86b7b945d34bfb2bc29a33ed411d2caaf763c63}{habi/zmk-tooth-cohort-method-manuscript@e86b7b9}
on December 21, 2020.
